Online {\IterComp}

### 2017-09-11 results.tex
overall updates
minor changes in results

\begin{figure*}[ht]
    \centering
    \includegraphics[width=\textwidth]{figs/num-probes.pdf}
    \caption{Percentage of instrumented basic blocks for the optimal and the relaxed instrumentation with different relaxation thresholds.}
    \label{fig:num-probes}
\end{figure*}

@@

For comparison, we use four configurations\footnote{A configuration using the WPO relaxation was not used due to the time necessary for executing the experiments.}.
In all configurations, the same optimization sequence is used for multiple inputs, using a dynamic input-window size, as explained in Section~\ref{sec:oic-infra}.
The average performance over the input window provides an estimate for the overall performance of the optimization sequence across distinct inputs.
The optimization sequences are ranked based on their average performance, and the best optimization sequence is selected.
%When selecting the best optimization sequence, they are ranked by the average of their performance measurement, using the WP metric, except for the Oracle-RM which uses the real speedup over \texttt{-O0}.
\begin{itemize}
\item \textbf{Oracle-RM} executes the program multiple times for each input, measuring the real speedup for each optimization sequence, and then uses the real speedup over {\flagstype -O0} for comparing the optimization sequences.
  The speedups are computed based on the wall-clock time.
  In order to reduce noise, the program is executed several times for the same input, until the confidence interval was no larger than 1\% for a 99\% confidence.
\item \textbf{Oracle-PP} represents an oracle with a \textit{perfect} non-intrusive profiling.
  Although it uses the WP metric for comparing optimization sequences, this oracle also avoids noise in its measurements by also executing the program multiple times for each input.
  The first execution is used for profiling the work metric.
  The remaining executions are used for measuring the wall-clock time without using the work profiling.
\item \textbf{Real-OP} corresponds to the online {\itercomp} as it would be applied in a real online scenario.
  For each optimization, a random sample of inputs is selected, and the program is executed only once with each input.
  When executing each input, it uses the optimal work instrumentation for profiling the work metric.
  The average of the WP for the sample of inputs is then used for selecting the best optimization.
\item \textbf{Real-R5} is similar to the {Real-OP}.
  It also corresponds to the online {\itercomp} as it would be applied in a real online scenario.
  For each optimization, a random sample of inputs is selected, and the program is executed only once with each input.
  When executing each input, it uses the relaxed work instrumentation, with a 5\% threshold, for profiling the work metric.
  The average of the WP for the sample of inputs is then used for selecting the best optimization.
\item \textbf{Real-IPC} corresponds to the online {\itercomp} based on the IPC metric.
  For each optimization, a random sample of inputs is selected, and the program is executed only once with each input.
  The average of the IPC metric for the sample of inputs is then used for selecting the best optimization.
\end{itemize}
The comparison between Oracle-RM and Oracle-PP is useful for validating the use of the WP metric for guiding {\itercomp}, while the other configurations demonstrate the viability of applying the online {\itercomp} in a real scenario.

>>>>

%\begin{figure*}[ht]
%    \centering
%    \includegraphics[width=\textwidth]{figs/num-probes.pdf}
%    \caption{Percentage of instrumented basic blocks for the optimal and the relaxed instrumentation with different relaxation thresholds.}
%    \label{fig:num-probes}
%\end{figure*}

@@

For comparison, we use four configurations\footnote{A configuration using the WPO relaxation was not used due to the time necessary for executing the experiments.}.
In all configurations, the same optimization sequence is used for multiple inputs, using a dynamic input-window size, as explained in Section~\ref{sec:oic-infra}.
The average performance over the input window provides an estimate for the overall performance of the optimization sequence across distinct inputs.
The optimization sequences are ranked based on their average performance, and the best optimization sequence is selected.
%When selecting the best optimization sequence, they are ranked by the average of their performance measurement, using the WP metric, except for the Oracle-RM which uses the real speedup over \texttt{-O0}.
\begin{itemize}
\item \textbf{Oracle-RM} executes the program twice for each input, measuring the real speedup for each optimization sequence, and then uses the real speedup over {\flagstype -O0} for guiding online {\itercomp}. This oracle provides a reference results for assessing the effectiveness work-efficiency metric.
\item \textbf{Oracle-PP} represents an oracle with a \textit{perfect} non-intrusive profiling.
  It uses the work-efficiency metric for guiding online {\itercomp}.
  Because this version simulates a \textit{perfect} profiling, with zero overhead,
  it allows us isolate and evaluate the effectiveness work-efficiency metric.
\item \textbf{Real-OP} corresponds to the online {\itercomp} as it would be applied in a real-world online scenario.
  The program is executed only once with each input.
  It uses the optimal work profiling for computing the work efficiency.
\item \textbf{Real-R5} is similar to the {Real-OP}, but with a relaxation of 5\% in the work profiling.
\item \textbf{Real-IPC} uses IPC for guiding the online {\itercomp}.
\end{itemize}
The comparison between Oracle-RM and Oracle-PP is useful for validating the use of the WP metric for guiding {\itercomp}, while the other configurations demonstrate the viability of applying the online {\itercomp} in a real scenario.
